A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Conscious settings
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1058 43ef1190-90fd-4dd7-a769-d0121f02b80e

We found that some implementations are likely better than others, but
further understanding of these differences are impeded by the fact
that most \httph{Server} headers contained very little
information. Future work could seek more sophisticated fingerprinting
and understanding of the nature of these differences.\todo{comment on
  conscious setting}

>>>>

We found that some implementations are likely better than others, but
further understanding of these differences are impeded by the fact
that most \httph{Server} headers contained very little
information. Future work could seek more sophisticated fingerprinting
and understanding of the nature of these differences. With this, it
may also be possible to investigate whether expiry times have been set
consciously.
